Interval Probability for Fuzzy Quantum Theories

### 2016-06-04 prob.tex
discreteGBKS.bib update citation...
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} start throwing some comments...

In previous section, the probability of each event is known
a priori. In reality, we seldom know much about events, but we could still assume
each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
be approximated to given accuracy by the relative
frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
$N$ goes to infinity. This fact is called the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

\subsection{Measuring Quantum Probabilities}
\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

\subsection{Quantum Interval-valued Probabilities Measures}
\cite{Vourdas2014, Vourdas2015}

>>>>

In previous section, the probability of each event is known
a priori. In reality, we seldom know much about events, but we could still assume
each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
be approximated to given accuracy by the relative
frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
$N$ goes to infinity. This fact is called the law of large
numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

%%%%%
\subsection{Measuring Quantum Probabilities}
\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}
\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
and highly readable until section IV. However, I don't understand
since the second sentence in section IV:
\begin{itemize}
\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
are upper probabilities.
\end{itemize}
I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
Consider the simplest example the subspace $H_{1}$ is the zero space
$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
respectively. The lower probability is $0$ makes sense, but I don't
understand why the upper probability is $1$. Because both the lower
and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
theory.

Start reading \cite{Vourdas2015}...}
